Accelerating Biomolecular Nuclear Magnetic Resonance Assignment with A*

### 2014-03-27 paper/tex/Paper.tex
image cite
bibtex stuff
We didn't increase runtime. We increased performance/decreased runtime.

\begin{figure}[H]
\begin{center}
\includegraphics{carbon}
\end{center}
\caption{Expected Carbon Shift Values} % TODO citation
\label{fig:carbon}
\end{figure}

@@

\subsection{Results}
\label{sub:results}
Our algorithm has been tested with NMR datasets of varying size from experiments conducted by Dr. Kilpatrick.  When compared to manually assigned data, the algorithm produces the same, optimal ordering of amino acids. Initially, we focused our research on accurate assignment at the cost of speed. Thus, at the start of our research our algorithm was only able to assign smaller datasets with a chain of ten to fifteen amino acids. Shifting our focus to optimizing the algorithm's speed while maintaining the accuracy we had managed to achieve, we were able to improve runtime. With the increased runtime, we were able to correctly assign forty amino acids in less than a minute. In future research, we plan to test with larger datasets, maximizing speed and efficiency to the point that our algorithm can assign full protein sequences. We also plan to look into testing datasets with more than a few missing data points to verify that our algorithm correctly places amino acids when given less perfect data.

\subsection{Future Goals} % (fold)
\label{sub:future_goals}
In future research, we will look into maximizing speed and efficiency to the point that our algorithm can assign full amino acid sequences. In order to achieve this, we will experiment with  both parallelization (techniques) and machine learning. The latter of these two will assist in optimizing the cost calculation while the former will increase the speed of assignment. We believe these implementations will help our algorithm handle datasets with numerous missing data points, validating our results even when given incomplete data. 
% subsection future_goals (end)
\nocite{guntert_automated_2009}
\nocite{brief_introduction_Poulsen}
% section method (end)
\bibliographystyle{amc}
\bibliography{Paper}

>>>>

\begin{figure}[H]
\begin{center}
\includegraphics{carbon}
\end{center}
\caption{Expected Carbon Shift Values \cite{carbon}} % TODO citation
\label{fig:carbon}
\end{figure}

@@

\subsection{Results}
\label{sub:results}
Our algorithm has been tested with NMR datasets of varying size from experiments conducted by Dr. Kilpatrick.  When compared to manually assigned data, the algorithm produces the same, optimal ordering of amino acids. Initially, we focused our research on accurate assignment at the cost of speed. Thus, at the start of our research our algorithm was only able to assign smaller datasets with a chain of ten to fifteen amino acids. Shifting our focus to optimizing the algorithm's speed while maintaining the accuracy we had managed to achieve, we were able to improve runtime. With the increased performance, we were able to correctly assign forty amino acids in less than a minute. In future research, we plan to test with larger datasets, maximizing speed and efficiency to the point that our algorithm can assign full protein sequences. We also plan to look into testing datasets with more than a few missing data points to verify that our algorithm correctly places amino acids when given less perfect data.

\subsection{Future Goals} % (fold)
\label{sub:future_goals}
In future research, we will look into maximizing speed and efficiency to the point that our algorithm can assign full amino acid sequences. In order to achieve this, we will experiment with  both parallelization (techniques) and machine learning. The latter of these two will assist in optimizing the cost calculation while the former will increase the speed of assignment. We believe these implementations will help our algorithm handle datasets with numerous missing data points, validating our results even when given incomplete data. 
% subsection future_goals (end)
\nocite{*}
% section method (end)
\bibliographystyle{amc}
\bibliography{Paper}
